Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-25 tex/results.tex
change bibstyle

To generate the meshes for these simulations, we initially used the open source software Trimesh 
(\url{https://github.com/mikedh/trimesh}), but we realized that it was not producing a 
uniform mesh and that it was not possible to obtain regular triangles with the functions 
available when having a prism. To overcome this, we created our own mesh using Python scripts,
and obtained uniform meshes. We wanted to study the effect of a uniform mesh as well as the effect
of rounding the edges---Rockstuhl et al.\ mentioned rounded edges
as a factor that introduces extra peaks on the response. We were unable to control the 
roundness as a function of arc of curvature or the dimensions of the rectangular prism, so we 
decided to use the default settings on Trimesh. Figure \ref{fig:tri_reg_round_14} shows the 
results of the effect of uniformity and roundness. One can see that the second peak is not
present in the green curve, which can be attributed to the effect of the roundness. This is 
consistent with the results in Rockstuhl et al.

@@

Once we have found the ``best'' possible geometry construction, we show how our results 
(green curve in Figure \ref{fig:tri_reg_round_14}) compare 
with the original results from Rockstuhl's Figure 14. We have obtained Rockstuhl's curves by using 
the WebPlotDigitizer (\url{https://apps.automeris.io/wpd/}). The replication results are 
presented in Figure \ref{fig:rep_14}: the main peaks presented in Rockstuhl et al.\ are 
successfully replicated. While we still have the presence of a third peak in our results, we conjecture 
that this is a consequence of the 3D effects in our geometry.

>>>>

To generate the meshes for these simulations, we initially used the open source software Trimesh 
(\url{https://github.com/mikedh/trimesh}), but we realized that it was not producing a 
uniform mesh and that it was not possible to obtain regular triangles with the functions 
available when having a prism. To overcome this, we created our own mesh using Python scripts,
and obtained uniform meshes. We wanted to study the effect of a uniform mesh as well as the effect
of rounding the edges---Rockstuhl et al.\ mentioned rounded edges
as a factor that introduces extra peaks on the response. We were unable to control the 
roundness as a function of arc of curvature or the dimensions of the rectangular prism, so we 
decided to use the default settings on Trimesh. 
For reproducibility purposes, we provide all the mesh files, as described in sub-section \ref{sec:reprod}.
Figure \ref{fig:tri_reg_round_14} shows the 
results of the effect of uniformity and roundness. One can see that the second peak is not
present in the green curve, which can be attributed to the effect of the roundness. This is 
consistent with the results in Rockstuhl et al.

@@

Once we have found the ``best'' possible geometry construction, we show how our results 
(green curve in Figure \ref{fig:tri_reg_round_14}) compare 
with the original results from Rockstuhl's Figure 14. We obtained data from Rockstuhl's curves by using 
the WebPlotDigitizer (\url{https://apps.automeris.io/wpd/}). The replication results are 
presented in Figure \ref{fig:rep_14}: the main peaks presented in Rockstuhl et al.\ are 
successfully replicated. While we still have the presence of a third peak in our results, we conjecture 
that this is a consequence of the 3D effects in our geometry.
